Diffusive Homeostasis in a Self-Organizing Recurrent Neural Network \\ \begin{large} Spatially dependent Interaction as a Determinant of Neural Activity and Plasticity \end{large}

### 2016-12-12 draft.tex
.

Obviously, the appropriate choice of $NO_0$ is crucial for the goal of achieving and maintaining a certain level of activity. However, one cannot directly set a parameter of the model to the desired population activity, as it was the case for canonical intrinsic homeostasis. Rather, one needs to determine the average concentration \textit{associated} with the desired activity and set it as a target concentration. Though it is possible to derive this relation in an analytic fashion, for practical purposes of the simulation, we let the system run with the previous homeostatic mechanism, still solving equation \eqref{Ca_dyn}-\eqref{NO_dyn} until a steady mean over the concentrations at the neurons' positions was reached. This mean was then set to be the target concentration and we switched to diffusive homeostasis. Table \ref{Params_IP} summarizes the choice of parameters that where introduced in this section.
\begin{table}
\begin{tabular}{|l|l|}
\hline
\textbf{parameter} & \textbf{value} \\
\hline
$\mathrm{r_{IP}}$ & $\mathrm{3\;Hz}$ \\
\hline
$\mathrm{\eta_{IP}}$ & $\mathrm{0.1\;mV}$ \\
\hline
$\mathrm{Ca^{2+}_{spike}}$ & 1 \\ \hline
$\mathrm{\tau_{Ca^{2+}}}$ &  $\mathrm{10\;ms}$ \\
\hline
$\mathrm{\tau_{nNOS}}$ & $\mathrm{100\;ms}$ \\
\hline
$\mathrm{D}$ & default: 12500 $\mathrm{\mu m^2 s^{-1}}$ \\
\hline 
$\mathrm{\lambda}$ & $\mathrm{0.1\;s^{-1}}$ \\
\hline
$\mathrm{\tau_{V_t}}$ & see section \ref{activ_analys} \\
\hline
\end{tabular}
\caption{Parameters of homeostatic intrinsic plasticity.}
\label{Params_IP}
\end{table}

@@

\subsubsection{Distribution of Firing Rates}

>>>>

Obviously, the appropriate choice of $NO_0$ is crucial for the goal of achieving and maintaining a certain level of activity. However, one cannot directly set a parameter of the model to the desired population activity, as it was the case for canonical intrinsic homeostasis. Rather, one needs to determine the average concentration \textit{associated} with the desired activity and set it as a target concentration. Though it is possible to derive this relation in an analytic fashion, for practical purposes of the simulation, we let the system run with the previous homeostatic mechanism, still solving equation \eqref{Ca_dyn}-\eqref{NO_dyn} until a steady mean over the concentrations at the neurons' positions was reached. This mean was then set to be the target concentration and we switched to diffusive homeostasis. Table \ref{Params_IP} summarizes the choice of parameters that where introduced in this section.
\begin{table}
\begin{tabular}{|l|l|}
\hline
\textbf{parameter} & \textbf{value} \\
\hline
$\mathrm{r_{IP}}$ & $\mathrm{3\;Hz}$ \\
\hline
$\mathrm{\eta_{IP}}$ & $\mathrm{0.1\;mV}$ \\
\hline
$\mathrm{Ca^{2+}_{spike}}$ & 1 \\ \hline
$\mathrm{\tau_{Ca^{2+}}}$ &  $\mathrm{10\;ms}$ \\
\hline
$\mathrm{\tau_{nNOS}}$ & $\mathrm{100\;ms}$ \\
\hline
$\mathrm{D}$ & default: 10000 $\mathrm{\mu m^2 s^{-1}}$ \\
\hline 
$\mathrm{\lambda}$ & $\mathrm{0.1\;s^{-1}}$ \\
\hline
$\mathrm{\tau_{V_t}}$ & see section \ref{activ_analys} \\
\hline
\end{tabular}
\caption{Parameters of homeostatic intrinsic plasticity.}
\label{Params_IP}
\end{table}

@@

\subsubsection{Distribution of Firing Rates}
Achieving a broad distribution of firing rates among neurons was the core motivation for the implementation of diffusive homeostasis. Figure \ref{Fir_Rate_Dist_Compare} shows a first result, comparing both homeostatic mechanisms. As expected, non-diffusive homeostasis leads to a sharp distribution of firing rates at 3 Hz. Diffusive homeostasis indeed results in a much broader distribution of mean firing rates.  
\begin{figure}
\includegraphics[width=\textwidth]{../../plots/firing_rate_dists/fir_rate_dist_compare.png}
\caption{Histograms of mean firing rates over the excitatory population, regular (A) and logarithmic space (B). For diffusive homeostasis ($\mathrm{D=1000\, \mu m^2 s^{-1}}$), the distribution was generated from 10 simulation runs, 1 simulation was used for non-diffusive homeostasis. Mean firing rates where calculated from spikes within $\mathrm{t=1000-1500\,s}$.}
\label{Fir_Rate_Dist_Compare}
\end{figure}
